The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
added rOpenSci ref and comment
tried to improve related work; added a comment

While not a strictly machine-readable solution, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.

In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.

Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
These include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.

@@

\asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}

>>>>

In recognition of the general desire to improve rates software citation, funders and agencies in both the US (NFS, NIH and private foundations) and the UK (STFC, JISC, Wellcome Trust) have hosted (and sponsored) a number of workshops specifically aimed at addressing issues around software citation~\cite{Sufi:2014en,Ahalt:2015ve,ssisoftwarecredit,aas-software-index,saga,Allen:2015ub}.
\knnote{Anything we can say to tie these together? What didn't they do?}

Complementary efforts to provide credit for software development in research also depend on standardized citation practices.
In an effort to ease the process of citing software, Wilson suggested that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}.
However, this is not a strictly machine-readable solution.
Other proposals include the transitive credit via JSON-LD scheme~\cite{Katz:2015aa} that assigns varying credit weights to contriponents---both contributors and research artifacts, including software and data---depending on their level of importance to the work.
The Project CRediT (contributor role taxonomy) scheme~\cite{project_credit} includes a ``software'' category for authors of a publication with roles dedicated to software development, maintenance, and\slash or testing.
The related PaperBadger project~\cite{PaperBadger} offers digital contributor badges associated with each role, connecting publications with people via DOI and ORCID, respectively.

@@

\asnote{For key challenge `Determine standard practices for peer review of software':  we could cite the rOpenSci review process here: http://ropensci.org/blog/2016/03/28/software-review?}
\knnote{Yes, absolutely! I went ahead and added a ref for you :)}
\cite{rOpenSci-reviews}
